Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
update the figure and comments

\sergey{Future version, extensions, declarative stuff, bla-bla here}

>>>>

\sergey{Future version, extensions, declarative stuff, bla-bla here}
discussion: what would be a language to extend the system, what would be the user interface? can it be used by community?  can it be complitely automated? interaction with user and highlighing?

conclusions 
points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
